Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller{Petersburg version \YellowPaperVersionNumber}

### 2020-05-11 Paper.tex
Don't show version on every page header as it obscures page numbers

\title{Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Petersburg version \YellowPaperVersionNumber}}}
\author{
    Dr. Gavin Wood\\
    Founder, Ethereum \& Parity\\
    gavin@parity.io
}
\begin{document}

>>>>

\title[Ethereum: A Secure Decentralised Generalised Transaction Ledger]{Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller{Petersburg version \YellowPaperVersionNumber}}
\author{
    Dr. Gavin Wood\\
    Founder, Ethereum \& Parity\\
    gavin@parity.io
}
\begin{document}
